---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Open+Sans:wght@300..800&family=Roboto&display=swap');

body {
  font-family: 'Open Sans', sans-serif;
  background: linear-gradient(to bottom, #f2f2f2, #e0e0e0);
}

h2 {
  font-weight: bold;
}

img {
  display: block;
  margin: auto;
  width: 50%;
  border: 5px solid #000000;
  border-radius: 10px;
}

a {
  color: #a2bffe;
  text-decoration: none;
  font-weight: bold;
  transition: color 0.5s ease-in-out;
}

.figcaption {
  text-align: center;
  font-style: italic;
}

.content-box {
  max-width: 75%;
  margin: auto;
  padding: 2rem;
  background-color: white;
  border-radius: 10px;
}

```
<div class="content-box">
## YouTube thumbnail analysis

This dynamic report observes patterns in how YouTube thumbnails are designed based off the category of the video.
Below, I have focused on two key ideas to look out for - how clickbaity the thumbnails are in each different category, and how visually complex the thumbnails are. 

### Average clickbait value sorted by video category

```{r}
library(tidyverse)

# original data logged from Google forms
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSB5uWBQ7zIPmwYYxTWnseFjsoVWPTGBp4nYuq2b4FMHCtaMSnTWFKiYo3wRrKRmMv1QmnkJKc9aQB_/pub?gid=1101770303&single=true&output=csv")

# rename variables & create new data frame
latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    video_category = `What kind of YouTube video is the thumbnail suggesting?`,
    has_faces = `Are there people/faces visible on the thumbnail?`,
    clickbait_score = `On a scale from 0 to 10, with 10 being very "clickbaity", how "clickbait" is the thumbnail? (How exaggerated/sensationalized/misleading) is the thumbnail?`,
    visual_complexity = `How visually complex is the YouTube thumbnail? With 1 Being minimal/less cluttered, and 5 being very cluttered, with many things present in the thumbnail.`
  )

# identifying summary values
mean_clickbait_score = mean(latest_data$clickbait_score)
median_clickbait_score = median(latest_data$clickbait_score)

# Mean click score sorted by category
latest_data %>%
  group_by(video_category) %>%
  summarise(avg_clickbait = mean(clickbait_score)) %>% 
  ggplot() +
  geom_bar(aes(x = video_category, y = avg_clickbait), stat = "identity") +
  geom_hline(yintercept = mean_clickbait_score, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = mean_clickbait_score + 0.3, label = "Overall Avg Clickbait Score") +
  geom_hline(yintercept = median_clickbait_score, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = median_clickbait_score + 0.3, label = "Median Clickbait Score") +
  labs(title = "Average Clickbait Value by Video Category",
       subtitle = "How exaggerated/sensationalized/misleading the thumbnails are for each category of YouTube videos.",
       x = "Video Category",
       y = "Avg Clickbait Score")

```


The mean clickbait score across all of the video categories is `r round(mean_clickbait_score, 1)`,
and the median clickbait score across all the video categories is `r round(median_clickbait_score, 1)`.

### Average visual complexity of YouTube thumbnails, sorted by the video category
```{r}
library(tidyverse)

# original data logged from Google forms
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSB5uWBQ7zIPmwYYxTWnseFjsoVWPTGBp4nYuq2b4FMHCtaMSnTWFKiYo3wRrKRmMv1QmnkJKc9aQB_/pub?gid=1101770303&single=true&output=csv")

# rename variables & create new data frame
latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    video_category = `What kind of YouTube video is the thumbnail suggesting?`,
    has_faces = `Are there people/faces visible on the thumbnail?`,
    clickbait_score = `On a scale from 0 to 10, with 10 being very "clickbaity", how "clickbait" is the thumbnail? (How exaggerated/sensationalized/misleading) is the thumbnail?`,
    visual_complexity = `How visually complex is the YouTube thumbnail? With 1 Being minimal/less cluttered, and 5 being very cluttered, with many things present in the thumbnail.`
  )

# identifying summary values
median_clickbait_score = median(latest_data$clickbait_score)
mean_visual_complexity = mean(latest_data$visual_complexity)

# Thumbnail complexity by video category
latest_data %>%
  group_by(video_category) %>%
  summarise(avg_complexity = mean(visual_complexity)) %>%
  ggplot() +
  geom_bar(aes(x = video_category, y = avg_complexity), stat = "identity") +
  geom_hline(yintercept = mean_visual_complexity, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = mean_visual_complexity + 0.3, label = "Overall Avg Visual Complexity") +
  labs(title = "Average Visual Complexity of YouTube Thumbnails by Video Category",
       subtitle = "How visually complex (minimal/not very cluttered vs very cluttered) the thumbnails are for each category of YouTube videos.",
       x = "Video Category",
       y = "Avg Visual Complexity")
```


The mean visual complexity score across all of the video categories is `r round(mean_visual_complexity, 1)`. 
</div>
